\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-06-26 doc/sui14/interaction.tex
updated the system architecture figure

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/architecture}
\caption{In our system architecture, selection is initiated through infrared but confirmed over 802.15.4. This permits wearers to move their head freely after connecting to an appliance. In the research prototype, users have to carry an additional microcontroller board that marshals messages between Glass' Bluetooth radio an IR/802.15.4, but our custom hardware could also be integrated into the wearable device.}
\label{fig:architecture}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=1\columnwidth]{figures/architecture_new}
\caption{Our System architecture diagram. The selection is initiated through infrared but confirmed over 802.15.4.}
\label{fig:architecture}
\end{figure}
